A game theoretic model of the behavioural gaming that takes place at the EMS - ED interface\tnoteref{t1}

### 2022-03-29 sections/queueing_model/waiting_time/main.tex
Apply suggestions from Vince's review
Co-authored-by: Vince Knight <vince@vknight.org>

Figure \ref{fig:markov_vs_des_waiting_time_comparison_overall} shows a 
comparison between the calculated mean waiting time using Markov chains and the
simulated waiting time using discrete event simulation over a range of values of 
\(\lambda_2\) (details of the discrete event simulation model are given in 
appendix~\ref{sec:appendix_des}).
The figure is used to demonstrate the accuracy of the waiting time formula of
the constructed queueing model as well as the effect of truncating the model.
The simulation was ran 100 times and the recorded mean waiting time at each 
iteration is used to populate the violin plots.
In detail, figure \ref{fig:markov_vs_des_waiting_time_comparison_overall} shows
the calculated mean waiting time using Markov chain, using a truncated 
simulation and using a simulation with infinite capacity (without the artificial
parameters \(N\) and \(M\)).
Each plot corresponds to different values of \(N\) and \(M\) and is ran over 
different values of \(\lambda_2\).
The untruncated simulation values (blue) are the same at all three graphs since
the effect of truncation does not apply to it.
The waiting times generated by the truncated simulation match the ones generated 
by the Markov chains model.
Note that this comparison includes both type 1 and type 2 individuals.
A separate comparison of only type 1 and only type 2 individuals can be found 
in appendix~\ref{sec:appendix_additional_figures}.

>>>>

Figure \ref{fig:markov_vs_des_waiting_time_comparison_overall} shows a 
comparison between the calculated mean waiting time using Markov chains and the
simulated waiting time using discrete event simulation over a range of values of 
\(\lambda_2\) (details of the discrete event simulation model are given in 
appendix~\ref{sec:appendix_des}).
The figure is used to demonstrate the accuracy of the waiting time formula of
the constructed queueing model as well as the effect of truncating the model.
The simulation was ran 100 times and the recorded mean waiting time at each 
iteration is used to populate the violin plots.
In detail, figure \ref{fig:markov_vs_des_waiting_time_comparison_overall} shows
the calculated mean waiting time using the Markov chain, using a truncated 
simulation and using a simulation with infinite capacity (without the artificial
parameters \(N\) and \(M\)).
Each plot corresponds to different values of \(N\) and \(M\) and is run over 
different values of \(\lambda_2\).
The untruncated simulation values are the same at all three graphs since
the effect of truncation does not apply to it.
The waiting times generated by the truncated simulation match the ones generated 
by the Markov chains model.
Note that this comparison includes both type 1 and type 2 individuals.
A separate comparison of only type 1 and only type 2 individuals can be found 
in appendix~\ref{sec:appendix_additional_figures}.
